Viscous Transport in Eroding Porous Media

### 2019-05-31 docs/transport/erosion_transport.tex
do the result section in transport paper

To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points. The following is the four-step fast summation methods.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

@@

{\color{red}
 Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
\begin{equation}\label{eqn:Cw2b}
d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}
\end{equation}
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
\begin{equation}\label{eqn:Cb2b}
d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
\end{equation}
where $\alpha_2$ is a constant.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. Let the initial radius of the body be $r$, the initial length of the body be $L$, 
and $d$ be the minimum initial distance from body to wall. Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer boundary and discretization points on the bodies, respectively.  We fix $N_\out=1024$ for all the simultions. We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}. We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in the shear flow. 
This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
The initial velocity of flow from the left side of $\Omega$ is 
$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
We place a single eroding body close to the no-slip wall ($y=-1$).
This example has no pressure drop. 
We investigate the shape of eroding body when it is close to a solid wall at the three  
distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .

@@

The snapshots of the process of 20 nearly touching bodies 
eroding are in Fig.~\ref{fig:Eroding20vort}. 
We initially place some bodies to nearly contact not only one another 
but also the outer boundary. For example, bodies 1, 6, 13, and 15 
are very close to outer boundary. In~\cite{qua-moo2018} 
we reported the quick expanding space at the narrow channel 
between neighboring bodies, the developing flat faces at the sites 
of near contact, and bodies vanishing. In this nearly touching bodies 
structure, we also observe these similar phenomena but not totally the same.
For the speed of expanding space at the narrow channel, we see some 
narrow channels do expand faster than other wider channels. 
For example, the spacing between bodies 14 and 18 is smaller 
than the spacing between bodies 7 and 14 initially and the former one is 
comparable to the latter one by the second frame. But there are some 
small initial spacings that do not expand that much at all by the fourth frame, 
for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the vorticity of fluid 
in Fig.~\ref{fig:Eroding20vort}. 
Since the eroding velocity on the body is proportional to the 
absolute value of vorticity in our erosion model,  
then when the  absolute value of vorticity is small 
there is not much erosion on the body. 
In all four frames of Fig.~\ref{fig:Eroding20vort}, 
the vorticity is relatively small between bodies 1 \& 6 and 3 \& 9.

Besides the channels between two bodies, there is a single channel 
goes across the domain horizontally and
 the flow has been concentrated in this channel. 
In the second frame of Fig.~\ref{fig:Eroding20vort},
 this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
We can get a better understanding of this channel from 
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
the flow (or tracer) first comes from three small channels 
between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
then the three branches become one and go into the main channel between bodies 1 \& 9. 
From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
this channel is expanding faster than other channel 
and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
The reason of fast expansion of this channel is the high vorticity. 
In the forth frame of Fig.~\ref{fig:Eroding20vort}, 
we could see the vorticity is relatively high on the side of bodies which form this channel
so the bodies are eroded fast on the side of this channel or have vanished completely.

@@

For the flat faces at the sites of near contact, since we put the body be close to one another
so we are able to see all the channels between two close bodies have flat faces. 
Besides the channels between bodies, we also observe the flat faces on the bodies 
which are close to the outer boundary. For example, we see the flat faces 
on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.

@@

In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding. At the beggining, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing

@@

\subsection{100 bodies}
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow.
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer wall with $N_\out$ points. The following is the four-step fast summation methods.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

@@

{\color{red}
 Let $L_w$ be the length of the outer wall and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer wall to body,  let $d$ be the minimum distance between outer wall and a point $x$ on the body $b$, we say $x$ is too close to outer wall if
\begin{equation}\label{eqn:Cw2b}
d< \alpha_1\frac{L_w}{N_\out}
\end{equation}
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
\begin{equation}\label{eqn:Cb2b}
d<\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
\end{equation}
where $\alpha_2$ is a constant.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. Let the initial radius of the body be $r$, the initial length of the body be $L$, 
and $d$ be the minimum initial distance from body to wall. Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer wall and discretization points on the bodies, respectively.  We fix $N_\out=1024$ for all the simultions. We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}. We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in the shear flow. 
This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
The initial velocity of flow from the left side of $\Omega$ is 
$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
We place a single eroding body close to the no-slip wall ($y=-1$).
This example has no pressure drop. 
We investigate the shape of eroding body when it is close to a solid wall at the three  
distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .

@@

The snapshots of the process of 20 nearly touching bodies 
eroding are in Fig.~\ref{fig:Eroding20vort}. 
We initially place some bodies to nearly contact not only one another 
but also the outer wall. For example, bodies 1, 6, 13, and 15 
are very close to outer wall: 
the distance between body 1 and outer wall is $1.3025h$, 
the distance between body 6 and outer wall is $2.9275h$,
the distance between body 13 and outer wall is $2.8447h$,
the distance between body 15 and outer wall is $1.3352h$ 
where $h=L_w/N_\out$ is the arclength spacing correponding to the outer wall.
 In~\cite{qua-moo2018} 
we reported the quick expanding space at the narrow channel 
between neighboring bodies, the developing flat faces at the sites 
of near contact, and bodies vanishing. In this nearly touching bodies 
structure, we also observe these similar phenomena but not totally the same.
For the speed of expanding space at the narrow channel, we see some 
narrow channels do expand faster than other wider channels. 
For example, the spacing between bodies 14 and 18 is smaller 
than the spacing between bodies 7 and 14 initially and the former one is 
comparable to the latter one by the second frame. But there are some 
small initial spacings that do not expand that much at all by the fourth frame, 
for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the vorticity of fluid 
in Fig.~\ref{fig:Eroding20vort}. 
Since the eroding velocity on the body is proportional to the 
absolute value of vorticity in our erosion model,  
then when the  absolute value of vorticity is small 
there is not much erosion on the body. 
In all four frames of Fig.~\ref{fig:Eroding20vort}, 
the vorticity is relatively small between bodies 1 \& 6 and 3 \& 9.

Besides the channels between two bodies, there is a single channel 
goes across the domain horizontally and
 the flow has been concentrated in this channel. 
In the second frame of Fig.~\ref{fig:Eroding20vort},
 this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
We can get a better understanding of this channel from 
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
the flow (or tracer) first comes from three small channels 
between outer wall \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
then the three branches become one and go into the main channel between bodies 1 \& 9. 
From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
this channel is expanding faster than other channel 
and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
The reason of fast expansion of this channel is the high vorticity. 
In the forth frame of Fig.~\ref{fig:Eroding20vort}, 
we could see the vorticity is relatively high on the side of bodies which form this channel
so the bodies are eroded fast on the side of this channel or have vanished completely.

@@

For the flat faces at the sites of near contact, since we put the body be close to one another
so we are able to see all the channels between two close bodies have flat faces. 
Besides the channels between bodies, we also observe the flat faces on the bodies 
which are close to the outer wall. For example, we see the flat faces 
on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.

@@

In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing when more and more bodies are vanished in the fluid.

@@

\subsection{100 bodies}
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow.
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer wall, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
